CDSR Human Data/Modelling Paper

### 2013-09-07 code/scenarios/cdsr/trunk/papers/ACS2013/main.tex
JK added to likert scale section

The type 2 trials the same visual stimuli and accompanying spatial descriptions as the type 1 trials with the addition that a location was marked on the visual stimuli (using a red dot) and the subject was asked to rank on a five point likert scale their judgement of how well the location matched the described spatial region. For each stimuli domain (classroom, map, military engagement) three points were pre-selected such that for each particular stimuli one of the points was located near the expected prototypical center of the described spatial region and the other two points were at varying distances from this location. For clarity it is worth emphaising that, although the same three points were used for all the stimuli from a particular domain, the particular point that acted as the sweetspot for a particular stimuli within a domain set would vary from stimuli to stimuli. The selection of these points was informed by the results of a pilot study. Figure \ref{fig:locations} illustrates the points selected for each domain and overlays them on one of the visual stimuli from each domain. Table \ref{tab:point-likert-scores} list the average likert scores for the different points in each domain. In the map domain the points are named from top-left to bottom-right (e.g., $Pt1$ is the point in the top left of Figure \ref{fig:bottleneck-points}); in the classroom domain the points are named in order from left to right (e.g. $Pt1$ is the leftmost point marked in Figure \ref{fig:classromm-points}); and, in the military engagment domain the points are named from top to bottom (e.g., $Pt1$ is the point nearest the top of Figure \ref{fig:tanks-points}).

@@

\begin{table}
\centerline{
\begin{tabular}{l c c c l}
\hline
Domain & \multicolumn{4}{c}{Map/Bottleneck} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} & Sweetspot\\
Stim ID & P1 & P2 & P3 & Significance\\
(g) & $1.1707$ & $\mathbf{4.6667}$ & $1.85$ & ToDo\\ % 1_1
(h) & $1.1707$ & $\mathbf{4.7561}$ & $1.585$ & ToDo\\ % 1_2
\hline
Domain & \multicolumn{4}{c}{Classrom/Front of Room} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} & Sweetspot\\
Stim ID & P1 & P2 & P3 & Significance\\
(a) & $\mathbf{3.5122}$ & $2.6341$ & $1.9024$ & ToDo\\ % 2_1
(c) & $\mathbf{4.7073}$ & $2.9024$ & $1.3571$ & ToDo\\ % 2_6
(c-flipped) & $1.244$ & $2.9268$ & $\mathbf{4.6429}$ & ToDo\\ %2_7
(e) & $\mathbf{4.7561}$ & $2.0000$ & $1.2439$ & ToDo\\ %2_2
(e-flipped) & $1.2439$ & $1.8500$ & $\mathbf{4.7073}$ & ToDo\\ % 2_3
(f) & $\mathbf{4.8292}$ & $2.0976$ & $1.2750$ & ToDo\\ % 2_4
(f-flipped) & $1.1463$ & $2.3171$ & $\mathbf{4.6585}$ & ToDo\\\\ % 2_5
\hline
Domain & \multicolumn{4}{c}{Military Engagement/Safe Region} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} & Sweetspot\\
Stim ID & P1 & P2 & P3 & Significance\\
(i) & $1.1951$ & $4.3902$ & $\mathbf{4.6428}$ & ToDo\\ % 3_1
(j) & $1.0952$ & $2.2927$ & $\mathbf{4.5122}$ & ToDo\\ % 3_2
(k) & $1.0714$ & $2.7804$ & $\mathbf{4.6585}$ & ToDo\\ % 3_3
(l) & $1.2327$ & $3.1667$ & $\mathbf{4.7073}$ & ToDo\\ % 3_4
\hline
\hline
\end{tabular}
}
\label{tab:point-likert-scores}
\caption{Need to put in caption!!!}
\end{table}

>>>>

The type 2 trials the same visual stimuli and accompanying spatial descriptions as the type 1 trials with the addition that a location was marked on the visual stimuli (using a red dot) and the subject was asked to rank on a five point likert scale their judgement of how well the location matched the described spatial region. For each stimuli domain (classroom, map, military engagement) three points were pre-selected such that for each particular stimuli one of the points was located near the expected prototypical center of the described spatial region and the other two points were at varying distances from this location. For clarity it is worth emphaising that, although the same three points were used for all the stimuli from a particular domain, the particular point that acted as the sweetspot for a particular stimuli within a domain set would vary from stimuli to stimuli. The selection of these points was informed by the results of a pilot study. Figure \ref{fig:locations} illustrates the points selected for each domain and overlays them on one of the visual stimuli from each domain. Table \ref{tab:point-likert-scores} list the average likert scores for the different points in each domain. In the map domain the points are named from top-left to bottom-right (e.g., $Pt1$ is the point in the top left of Figure \ref{fig:bottleneck-points}); in the classroom domain the points are named in order from left to right (e.g. $Pt1$ is the leftmost point marked in Figure \ref{fig:classromm-points}); and, in the military engagment domain the points are named from top to bottom (e.g., $Pt1$ is the point nearest the top of Figure \ref{fig:tanks-points}). For each stimuli we have highlighted in bold the maximum average likert rating for a point for that stimuli.

@@

\begin{table}
\centerline{
\begin{tabular}{l c c c l}
\hline
Domain & \multicolumn{4}{c}{Map/Bottleneck} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} & Sweetspot\\
Stim ID & P1 & P2 & P3 & Significance\\
(g) & $1.1707$ & $\mathbf{4.6667}$ & $1.85$ & ToDo\\ % 1_1
(h) & $1.1707$ & $\mathbf{4.7561}$ & $1.585$ & ToDo\\ % 1_2
\hline
Domain & \multicolumn{4}{c}{Classrom/Front of Room} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} & Sweetspot\\
Stim ID & P1 & P2 & P3 & Significance\\
(a) & $\mathbf{3.5122}$ & $2.6341$ & $1.9024$ & ToDo\\ % 2_1
(c) & $\mathbf{4.7073}$ & $2.9024$ & $1.3571$ & ToDo\\ % 2_6
(c-flipped) & $1.244$ & $2.9268$ & $\mathbf{4.6429}$ & ToDo\\ %2_7
(e) & $\mathbf{4.7561}$ & $2.0000$ & $1.2439$ & ToDo\\ %2_2
(e-flipped) & $1.2439$ & $1.8500$ & $\mathbf{4.7073}$ & ToDo\\ % 2_3
(f) & $\mathbf{4.8292}$ & $2.0976$ & $1.2750$ & ToDo\\ % 2_4
(f-flipped) & $1.1463$ & $2.3171$ & $\mathbf{4.6585}$ & ToDo\\\\ % 2_5
\hline
Domain & \multicolumn{4}{c}{Military Engagement/Safe Region} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} & Sweetspot\\
Stim ID & P1 & P2 & P3 & Significance\\
(i) & $1.1951$ & $4.3902$ & $\mathbf{4.9024}$ & ToDo\\ % 3_1
(j) & $1.0952$ & $2.2927$ & $\mathbf{4.5122}$ & ToDo\\ % 3_2
(k) & $1.0714$ & $2.7804$ & $\mathbf{4.6585}$ & ToDo\\ % 3_3
(l) & $1.2327$ & $3.1667$ & $\mathbf{4.7073}$ & ToDo\\ % 3_4
\hline
\hline
\end{tabular}
}
\label{tab:point-likert-scores}
\caption{Need to put in caption!!!}
\end{table}
